---
title: "Data Cleaning"
author: "Julie Norman"
date: "5/22/2018"
output: html_document
---

# Libraries
```{r}
library(readxl)
library(tidyr)
library(dplyr)
library(reshape2)
library(plm)
library(AER)

```

#Upload Data

```{r}
finaldata <- read_excel("~/Documents/Economics/Research/Minimum Wage Ski/Data Sources/final panel data.xlsx")
```


```{r}
finaldata$statefip <- as.factor(finaldata$statefip)
finaldata$countfip <- as.factor(finaldata$countfip)
finaldata$statecofip <- as.factor(finaldata$statecofip)

finaldata$category <- with(finaldata, interaction(finaldata$statefip,  finaldata$countfip))

finaldata$category <- factor(finaldata$category)

str(finaldata)
```



# Equation For All County Types 

## Difference-in-Differences Fixed Effects

```{r}
didFE <- plm(ln_n ~ urn + SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute,
  data = finaldata, index=c("category", "year"), model="within")

didFEb <- plm(ln_n ~ urn + SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute | . -urn  (+CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16 + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute+ discyouth + burdenedhh), data = finaldata, index=c("category", "year"), model="within")

summary(m1)

```


## Second Stage Least Square Difference in Differences


```{r}
slsDID <- plm(ln_n ~ urn + SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute | SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute  + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16 + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute + discyouth + burdenedhh, data = finaldata, index=c("category", "year"), model="within")

#m2 <- ivreg(ln_n ~urn + SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute| urn + SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute +CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16 + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute+ discyouth + burdenedhh, data = finaldata)

#m2 <- ivreg(ln_n ~ SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute + urn | SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute + discyouth + burdenedhh, data = finaldata)

#m2 <- ivreg(ln_n ~ SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute + urn | .-urn + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16 + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute+ discyouth + burdenedhh, data = finaldata)

summary(m2)
```


## Fixed Effects Log-Log

```{r}
feLgLg <- plm(ln_n ~ urn + SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+  ln_minwage + ln_medhhinc + hsgrad + bsdeg + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute,
  data = finaldata, index=c("category", "year"), model="within")

summary(m3)
```



## Second Stage Least Square Log-Log

```{r}
slsLgLg <- plm(ln_n ~ urn + SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+  ln_minwage + ln_medhhinc + hsgrad + bsdeg + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute | SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+  ln_minwage + ln_medhhinc + hsgrad + bsdeg + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute  + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16 + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute + discyouth + burdenedhh, data = finaldata, index=c("category", "year"), model="within")

summary(m4)
```


end: urn
exog: SKI CO Y11 Y12 Y13 Y14 Y15 Y16 Y11xCO Y12xCO Y13xCO Y14xCO Y15xCO Y16xCO ln_minwage ln_medhhinc hsgrad bsdeg black hspn povrateall eqfxsubprime incineq ln_medage avgcommute 
instrum: CO Y11 Y12 Y13 Y14 Y15 Y16 ln_minwage ln_medhhinc hsgrad bsdeg black hspn povrateall eqfxsubprime incineq ln_medage avgcommute  discyouth  burdenedhh


# Equations for SKI Counties 

## Difference-in-Differences Fixed Effects Ski

```{r}
didFE_SKI <- plm(ln_n ~ urn + SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute,
  data = finaldata, index=c("category", "year"), model="within", SKI ==1)

didFEb_SKI <- plm(ln_n ~ urn + SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute | . -urn  (+CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16 + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute+ discyouth + burdenedhh), data = finaldata, index=c("category", "year"), model="within", SKI == 1)

summary(m1)

```


## Second Stage Least Square Difference in Differences Ski


```{r}
slsDID_SKI <- plm(ln_n ~ urn + SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute | SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute  + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16 + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute + discyouth + burdenedhh, data = finaldata, index=c("category", "year"), model="within", SKI == 1)

#slsDID_SKI <- ivreg(ln_n ~urn + SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute| urn + SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute +CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16 + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute+ discyouth + burdenedhh, data = finaldata, SKI == 1)

#slsDID_SKI <- ivreg(ln_n ~ SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute + urn | SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute + discyouth + burdenedhh, data = finaldata, SKI == 1)

#slsDID_SKI <- ivreg(ln_n ~ SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute + urn | .-urn + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16 + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute+ discyouth + burdenedhh, data = finaldata, SKI == 1)

summary(m2)
```


## Fixed Effects Log-Log Ski

```{r}
feLgLg_SKI <- plm(ln_n ~ urn + SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+  ln_minwage + ln_medhhinc + hsgrad + bsdeg + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute,
  data = finaldata, index=c("category", "year"), model="within", SKI == 1)

summary(m3)
```


## Second Stage Least Square Log-Log Ski

```{r}
slsLgLg_SKI <- plm(ln_n ~ urn + SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+  ln_minwage + ln_medhhinc + hsgrad + bsdeg + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute | SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+  ln_minwage + ln_medhhinc + hsgrad + bsdeg + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute  + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16 + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute + discyouth + burdenedhh, data = finaldata, index=c("category", "year"), model="within", SKI == 1)

summary(m4)
```



# Equations for NonSKI Counties 

## Difference-in-Differences Fixed Effects nonSki

```{r}
didFE_nSKI <- plm(ln_n ~ urn + SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute,
  data = finaldata, index=c("category", "year"), model="within", SKI ==0)

didFEb_nSKI <- plm(ln_n ~ urn + SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute | . -urn  (+CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16 + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute+ discyouth + burdenedhh), data = finaldata, index=c("category", "year"), model="within", SKI == 0)

summary(didFE_nSKI)

```


## Second Stage Least Square Difference in Differences nonSki


```{r}
slsDID_nSKI <- plm(ln_n ~ urn + SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute | SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute  + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16 + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute + discyouth + burdenedhh, data = finaldata, index=c("category", "year"), model="within", SKI == 0)

#INCORRECT
##slsDID_nSKI <- ivreg(ln_n ~urn + SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute| urn + SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute +CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16 + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute+ discyouth + burdenedhh, data = finaldata, SKI == 0)

##slsDID_nSKI <- ivreg(ln_n ~ SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute + urn | SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute + discyouth + burdenedhh, data = finaldata, SKI == 0)

##slsDID_nSKI <- ivreg(ln_n ~ SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute + urn | .-urn + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16 + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute+ discyouth + burdenedhh, data = finaldata, SKI == 0)

summary(slsDID_nSKI)
```


## Fixed Effects Log-Log nonSki

```{r}
feLgLg_nSKI <- plm(ln_n ~ urn + SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+  ln_minwage + ln_medhhinc + hsgrad + bsdeg + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute,
  data = finaldata, index=c("category", "year"), model="within", SKI == 0)

summary(feLgLg_nSKI)
```


## Second Stage Least Square Log-Log nonSki

```{r}
slsLgLg_nSKI <- plm(ln_n ~ urn + SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+  ln_minwage + ln_medhhinc + hsgrad + bsdeg + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute | SKI + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+  ln_minwage + ln_medhhinc + hsgrad + bsdeg + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16+ Y11xCO+ Y12xCO + Y13xCO + Y14xCO + Y15xCO + Y16xCO + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute  + CO + Y11 + Y12 + Y13 + Y14 + Y15+ Y16 + ln_minwage + ln_medhhinc + hsgrad + bsdeg  + black + hspn + povrateall + eqfxsubprime + incineq + ln_medage + avgcommute + discyouth + burdenedhh, data = finaldata, index=c("category", "year"), model="within", SKI == 0)

summary(slsLgLg_nSKI)
```







